DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-03 paper/background.tex

The use of neural networks for end-to-end control of autonomous
driving was first demonstrated in late 1980s~\cite{Pomerleau1989},
using a small fully connected neural network; and subsequently in a
DARPA Autonomous Vehicle (DAVE) project in early
2000s~\cite{LeCun:04}, using a 6 layer convolutional neural network
(CNN); and most recently in NVIDIA's DAVE-2
project~\cite{Bojarski2016}, using 9 layer CNN. In all these projects,
the neural network models take raw image pixels as input and directly
produce steering control commands bypassing all intermediary steps and
hand-written rules in conventional robotics control approach. The
NVIDIA's latest effort reports that their trained CNN successfully
self-drive their modified cars in public roads without human
intervention~\cite{Bojarski2016}.

>>>>

The use of neural networks for end-to-end control of autonomous
car was first demonstrated in late 1980s~\cite{Pomerleau1989},
using a small 3-layer fully connected neural network; and subsequently
in a DARPA Autonomous Vehicle (DAVE) project in early
2000s~\cite{LeCun:04}, using a 6 layer convolutional neural network
(CNN); and most recently in NVIDIA's DAVE-2
project~\cite{Bojarski2016}, using 9 layer CNN. In all these projects,
the neural network models take raw image pixels as input and directly
produce steering control commands bypassing all intermediary steps and
hand-written rules in conventional robotics control approach. The
NVIDIA's latest effort reports that their trained CNN successfully
self-drive their modified cars in public roads without human
intervention~\cite{Bojarski2016}.
